\refstepcounter{subsection}\subsection*{\thesubsection\quad Timely}\label{subsec:DiscussionTimely}

The most costly algorithm in the protocol is the $ \PreProcess $. In the experiment, we demonstrate that within a time budget $ \tau $ of eight hours, we can initiate a database of megabyte size, with the use of the generic \acrshort{mpc}-based \acrshort{ps} protocol and without any parallelization of bitonic sort. Further, we estimate that with perfect parallelization and a time budget $ \tau $ of eight hours, a database of size $ 2^{393} $ bytes could be initiated. 

The limiting factor is the runtime of performing a private swap, being why the \acrshort{ot}-based private swap protocol is an important realization. Its efficiency is directly equivalent to the efficiency of $\text{\acrshort{ot}}^2_1$, which is among the most fundamental and most researched topics in secure computation. We approximate that it allows us to initiate a database in the gigabyte range if swapped with the generic \acrshort{mpc} \acrshort{ps} protocol in $ \PreProcess $. Providing an implementation to test the efficiency also answers the question about the efficiency of initiating the \acrshort{ps} protocol, something we have not addressed with the generic \acrshort{mpc}-based \acrshort{ps} protocol, which requires a new set of beaver's triples per execution. In our experiments, we assumed that the circuits were already pre-compiled, so for simplicity, we reused the same circuit thereby not factoring in the compilation time in our runtime. 

Regarding the semantic search, it does not meet our timely definition of exerting sublinear complexity in the transfers, and we demonstrated that its efficiency is limited to smaller database sizes. What we can take away from the experiment is that it is possible to support embedding dimensions from state-of-the-art \acrshort{llm}s. Outside the scope of this work is the accuracy of these models on our data. Therefore, the open question is, what the minimal required embedding dimension is to satisfy a privacy-preserving semantic search on the records? To answer this question is necessary for a proper efficiency assessment of a private semantic search protocol as the vector length directly affects the number of required operations.
